Effects of Tunable Hydrophobicity on the Collective Hydrodynamics of Janus Particles under Flows

### 2023-03-29 doc/PRF2022/PRF_main.tex
yny

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
\label{sec:governing_equations}
The governing equations are a system of partial differential equations for the position and orientation of
a collection of rigid JPs~\cite{Fu2022_JFM}. We first pose the Stokes
equations for the mobility problem giving the hydrodynamic interactions
for the particle suspension. The hydrophobic forces come from solving a
screened Laplace equation. Particle collisions are avoided through a
near-field, pair potential.

@@

We discretize~\eqref{eq:SL_BIE2}
and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2} using high-order
interpolation-based quadrature rules. Integrals that are smooth are
computed with the spectrally-accurate trapezoid rule, and
nearly-singular integrals, caused by close contact between two
particles, are computed with a high-order interpolation-based quadrature
rule~\cite{qua-bir2014}.

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Governing Equations: Hydrophobic Attraction Potential Mobility Problem} 
\label{sec:governing_equations}
The governing equations are a system of partial differential equations for the position and orientation of
a collection of rigid JPs~\cite{Fu2022_JFM}. We first pose the Stokes
equations for the mobility problem giving the hydrodynamic interactions
for the particle suspension. The hydrophobic forces come from solving a
screened Laplace equation. Particle collisions are avoided through a
near-field, pair potential for their steric interactions.

@@

We discretize~\eqref{eq:SL_BIE2}
and~\eqref{eq:vel_BLM_rep}--\eqref{eq:vel_BLM_rep2} using high-order
interpolation-based quadrature rules. Smooth integrals are
computed with the spectrally-accurate trapezoid rule, and
nearly-singular integrals, caused by close contact between two
particles, are computed with a high-order interpolation-based quadrature
rule~\cite{qua-bir2014}.
